---
title: "Deliverable 2025"
author: "Catharina Clark"
date: "2025-02-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



```{r iris}
<<<<<<< HEAD
iris_data <- read.csv("iris.csv")
summary(iris_data)
=======
captures <- read.csv("iris.csv")
summary(iris)
>>>>>>> 230f7644831639ea12e10b269ceef44bfccbfc48
```

## Plots
Plots of sepal width against length and petal width against length (accordingly).

```{r iris_data, echo=FALSE}
plot(x = iris_data$Sepal.Length, y = iris_data$Sepal.Width, main = "Sepal Length by Width", xlim = c(4,8.5), ylim = c(1.5,5), xlab = "Sepal Length (mm)", ylab = "Sepal Width (mm)")

<<<<<<< HEAD
plot(x = iris_data$Petal.Length, y = iris_data$Petal.Width, main = "Petal Length by Width", xlim = c(0,8), ylim = c(0,3), xlab = "Petal Length (mm)", ylab = "Petal Width (mm)")
=======
```{r iris, echo=FALSE}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width, main = "Sepal Length by Width", xlim = c(4,8.5), ylim = c(1.5,5), xlab = "Sepal Length (mm)", ylab = "Sepal Width (mm)")

plot(x = iris$Petal.Length, y = iris$Petal.Width, main = "Petal Length by Width", xlim = c(0,8), ylim = c(0,3), xlab = "Petal Length (mm)", ylab = "Petal Width (mm)")
>>>>>>> 230f7644831639ea12e10b269ceef44bfccbfc48
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.